Block bootstrap consistency\\under weak assumptions

### 2017-04-05 subs/ETr4/reply_3.tex
[#35/gfn] Address referee's snarky functional comments in response letter
[#32/Ems] Add response to referees
[#37/cite] add statement about attribution to referee letter
[#38/ui] Address referee 3's comment on LIE
Write up summary of changes for resubmission

@@

@@

@@

@@

>>>>

In addition to the changes listed below, I have rewritten the proof of
Lemma 6 and changed the part of the proof of Theorems 1 and 2 where
the lemma was invoked. Lemma 6's proof had ignored a key measurability
requirement that conflicted with the martingale difference sequence
arguments used in some of the key inequalities.

\section*{\hfill Specific points\hfill}

@@

  I have added a disclaimer. Thanks.

@@

  Yes; this part of the proof has been rewritten in response to
  another referee's comment, however.

@@

  Ok. My primary motivation in writing that statement was to avoid
  appearing to take credit for a standard argument in this
  literature. (I was asked to include these steps explicitly by an
  earlier referee.)  I have added a reference to Van der Vaart's
  (2000) textbook instead, since I've been unable to track down a
  specific citation for Poly\'a.

@@

  This first result has been cleaned up a little bit.

### 2017-04-05 subs/ETr4/reply_4.tex
[#38/ui] Address referee 4's comment on UI in theorem 1
Write up summary of changes for resubmission

>>>>

\strut

\noindent I have rewritten this part of the proof as well as a similar
construction in the proof of Theorem 2. Lemma 6's proof had ignored
one key measurability requirement and has been entirely rewritten as
well.

In addition, I have corrected several typos and made minor changes
suggested by the other referees.

### 2017-04-05 subs/ETr4/reply_ed.tex
Write up summary of changes for resubmission

>>>>

I have made the changes requested by the referees. In addition,
referee 4's concerns led me to reexamine Lemma 6 and I found a subtle
error in its proof --- the measurability requirements of some of the
variables used in the proof were inconsistent with the martingale
difference sequence arguments I was using. So I have substantially
rewritten the proof to use a different argument.

To make the review process easier, I have also included a pdf of the
paper with the changes since the last version highlighted. Thanks
again for the opportunity to revise this paper.

\noindent Best,
